Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-01-08 paper.qmd
Updated error computation

```{r}
#| label: fig-one-dens_clust-error
#| fig-height: 8
#| fig-width: 8
#| fig-pos: H
#| fig-cap: "All \\gD{} layouts exhibit high error in the sparse end. The three \\gD{} layouts are: (a) tSNE, (b) UMAP, and (c) PaCMaP, which represent a C-shaped dense cluster colored according to the high-dimensional absolute error. Darker colors indicate high error, while lighter colors indicate low error. Regardless of the NLDR method used, the dense end of the structure shows low error, whereas the sparse end displays high error."

>>>>

```{r}
#| label: fig-one-dens_clust-error
#| fig-height: 10
#| fig-width: 10
#| fig-pos: H
#| fig-cap: "All \\gD{} layouts exhibit high error in the sparse end. The three \\gD{} layouts are: (a) tSNE, (b) UMAP, and (c) PaCMaP, which represent a C-shaped dense cluster colored according to the high-dimensional absolute error. Darker colors indicate high error, while lighter colors indicate low error. Regardless of the NLDR method used, the dense end of the structure shows low error, whereas the sparse end displays high error."
